A generalized definition of multidimensional item response theory parameters

### 2022-10-21 output/paper_draft/paper_M2PLM_parameters.Rmd
Update with Mario's review (WIP)

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
A respondent is represented by vector $`r TRAIT_VEC_IN_LS`$,
with coordinates $`r TRAIT_VECTOR`$ in $`r LATENT_SPACE`$,
which is assumed to be a multivariate normal random variable:

@@

As in @reckase_difficulty_1985, the characteristic function of item
$`r ITEM_INDEX`$ according to the M2PL model is formulated as follows:

@@

being  
$`r IRF_M2PL`$ ($= `r IRF_ABBR`$ henceforth, for simplicity) the probability of
a positive response to item $`r ITEM_INDEX`$ for a given $`r TRAIT_VECTOR`$,  
$`r DISCR_VECTOR`$ a $`r N_DIMS`$-dimensional vector of
discrimination parameters, and  
$`r INTERCEPT_PARAM`$ an intercept parameter related to the location of the item
in the latent space.

@@

## Linear algebra of non-orthogonal coordinates
<!-- # TODO: To appendix, OR citation about these? -->

### Inner product

Let $`r INNER_PROD_EQ`$ be the inner product in $`r LATENT_SPACE`$, with
the positive-definite matrix $`r INNER_PROD_MATRIX`$ its inner product matrix.
We may apply a change of basis in $`r LATENT_SPACE`$ that results in a space
$`r LATENT_SPACE_STD`$ with the standard basis $`r LS_STD_BASIS_EQ`$.
Such a change of basis can be defined as

\begin{equation}
  `r BASIS_CHANGE`,                                          (\#eq:change-basis)
\end{equation}

@@

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example.R")
```

>>>>

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS_EQ`$.
A respondent is represented by vector $`r TRAIT_VEC_IN_LS`$,
which is assumed to be a multivariate normal random variable:

@@

According to the M2PL model, the probability of a positive response to item
$`r ITEM_INDEX`$ is

@@

where $`r DISCR_VECTOR`$ is a $`r N_DIMS`$-dimensional vector of discrimination
parameters, and $`r INTERCEPT_PARAM`$ an intercept parameter related to the
location of the item in the latent space.

@@

## Linear algebra of non-orthogonal coordinates

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
TODO: Incomplete in Mario's version, is it correct to say "in the latent space"?
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each baseis.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$, where $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

Let $`r BASIS_CHANGE_DEF`$ be the change of basis matrix; then, we have that

\begin{equation}
  `r BASIS_CHANGE`.                                          (\#eq:change-basis)
\end{equation}

The $`r DIM_INDEX`$-th column of $`r TRANSFORM_MATRIX`$

@@

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example_Tezza2018.R")
```
